---
output: github_document
---

# simplecountries

<!-- badges: start -->
<!-- badges: end -->

`simplecountries` is a simple R package that helps to convert alternative country names to common English. It only has the function `simple_country_name`. The main source is  [this wikipedia article](https://en.wikipedia.org/wiki/List_of_alternative_country_names) and the conversion table from `countrycode`.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

``` r
remotes::install_github("davidsjoberg/simplecountries")
```

## Example

This is a basic example:

```{r example}
library(simplecountries)

x <- c("Czech", "Great Britain", "Sverige", "U.K.")
simple_country_name(x)
```

## Use `countrycode` instead

Since `simplecountries` was made the mature package `countrycode` has introduced the function `countryname` which does the same thing but is probably better maintained. You probably want to you that package instead. More info [here](https://github.com/vincentarelbundock/countrycode).
